---
title: "Height CNV Association Study"
author: "Ian Wilson"
date: "15 December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
source(here("R","prepare.R"))
install.load(c("data.table", "qqman"))
```

We have downloaded a file with the CNV association results with height from the paper by  Mace *et al.*.   [CNV-association meta-analysis in 191,161 European adults reveals new loci associated with anthropometric traits](https://www.nature.com/articles/s41467-017-00556-x#MOESM2).

## Height

```{r read_height, cache=TRUE, echo=FALSE}
height <- fread(dropbox("height_CNV_association_41467_2017_556_MOESM2_ESM.csv"))
head(height)
height[,SNP := paste("cnv",1:nrow(height),sep="")]
```


Investigate the qq plots.

```{r manhattan, cache=TRUE, echo=FALSE}
## Simple of Manhattan plot of BMI
##plot(-log10(height$`Pvalue BMI`), col=height$CHR%%2+1)
## Simple plot of Height
##plot(-log10(height$pvalue_BMI), col=height$CHR%%2+1, main="Height")
##qq(height$pvalue_BMI)
##acf(height$F_DUP)
######################################################

opar <- par(mfrow=c(4,1), mar=c(3,3,2,1))

height$P <- height$`Pvalue BMI`
manhattan(height, main="BMI")

height$P <- height$`Pvalue Weight`
manhattan(height, main="Weight")

height$P <- height$`Pvalue Height`
manhattan(height, main="Height")

height$P <- height$`Pvalue Waist-Hip ratio`
manhattan(height, main="Waist-Hip Ratio")
par(opar)
```

These don't look great.


```{r quantile_plots, cache=TRUE}
opar <- par(mfrow=c(2,2), mar=c(3,3,2,1))
qq(height$`Pvalue BMI`, main="BMI")
qq(height$`Pvalue Weight`, main="Weight")
qq(height$`Pvalue Height`, main="Height")
qq(height$`Pvalue Waist-Hip ratio`, main="Waist Hip Ratio")
par(opar)
```

These markers should be a good place to start in looking for associations between CNV variants and the SNP directory.