---
title: "Comparison of Genome Wide CNV and SNP results"
output:
  html_document:
    df_print: paged
---


The document looks at a pair of genome wide SNP resutls, fo4r height and for schizophrenia and tries to see if the results 
are related in any way.  There is a manuscript that looks at this

> The genetic overlap between schizophrenia and height.  Schizophr Res. 2013. 151: 226–228.

But this doesn't really say anything.  Is there anything in these data?




```{r}
library(here)
source(here("R","prepare.R"))
install.load("ggplot2", "pander")
install.load.bioc("GenomicRanges")
load(here("output", "GWAS_scz_summary.rda"))
load(here("output", "remapped_cnv.rda"))
load(here("output","GWAS_height_summary.rda"))
```


```{r prepare_CNV}
gheight_cnv19 <- GRanges(height_cnv19$CHR, IRanges(height_cnv19$BP, width=1), 
                       p_height = height_cnv19$`Pvalue Height`, beta_height= height_cnv19$`Beta Height`, 
                       p_bmi = height_cnv19$`Pvalue BMI`, beta_bmi = height_cnv19$`Beta BMI`, 
                       fdel=height_cnv19$F_DEL, fdup = height_cnv19$F_DUP)

gscz.dup19 <- GRanges(seqnames=scz.dup19$CHR, IRanges(start=scz.dup19$BP, width=1), 
                    z=scz.dup19$z, p=scz.dup19$z_pval, f=scz.dup19$NCNV/41321, 
                    fcontrol =scz.dup19$UNAFF/20227 , n=scz.dup19$NCNV, fcase = scz.dup19$AFF/21094)

gscz.del19 <- GRanges(seqnames=scz.del19$CHR, IRanges(start=scz.del19$BP, width=1), z=scz.del19$z, 
                    p=scz.del19$z_pval, f=scz.del19$NCNV/41321, 
                    fcontrol =scz.del19$UNAFF/20227 , n=scz.del19$NCNV, fcase = scz.del19$AFF/21094)

rm(height_cnv19, scz.del19, scz.dup19)
```


```{r prepare_gwas, cache=TRUE}
  gscz_gwas <- GRanges(seqnames=GWAS_scz_summary$chr, IRanges(start=GWAS_scz_summary$bp, width=1, names=GWAS_scz_summary$snpid)
                     , or=GWAS_scz_summary$or, p=GWAS_scz_summary$p)
  gheight_gwas <- GRanges(seqnames=GWAS_height_summary$seqnames, 
                IRanges(start=GWAS_height_summary$pos, width=1, names=GWAS_height_summary$MarkerName),
                b=GWAS_height_summary$b, p=GWAS_height_summary$p)
rm(GWAS_scz_summary, GWAS_height_summary)
```

Find nearest SNPs to height CNVs

```{r}
near <- nearest(gheight_cnv19, gheight_gwas)
combined  <- cbind(as.data.frame(gheight_cnv19, row.names=NULL), as.data.frame(gheight_gwas[near], row.names=NULL))
combined[,c(3,4,5,12,14,15,16)] <- NULL
colnames(combined)[c(2,9)] <- c("start_cnv", "start_snp")
combined$distance <- cut(abs(combined$start_cnv-combined$start_snp),c(-1,1,10,100,1000,100000,1E8))
ggplot(combined[combined$distance=="(-1,1]",], aes(x=b, y=beta_height)) + geom_point(alpha=0.1)

count_height19 <- countOverlaps(gheight_cnv19, gheight_gwas)
table(count_height19)

pander(tb)
tb <- table(combined$beta_height>0, combined$b>0)
chisq.test(tb)
```

Find nearest SNPs to scz CNVs

```{r}
near <- nearest(gscz.del19, gscz_gwas)
sczdel  <- cbind(as.data.frame(gscz.del19, row.names=NULL), as.data.frame(gscz_gwas[near], row.names=NULL))
sczdel[,c(3,4,5,12,14,15,16)] <- NULL
colnames(sczdel)[c(2,9)] <- c("start_cnv", "start_snp")
sczdel$distance <- cut(abs(sczdel$start_cnv-sczdel$start_snp),c(-1,1,10,100,1000,100000,1E8))
table(sczdel$distance)
ggplot(sczdel[sczdel$distance=="(-1,1]",], aes(x=z, y=or)) + geom_point(alpha=0.1)
tb <- table(sczdel$z>0, sczdel$or>1)
chisq.test(tb)
```

```{r}
near <- nearest(gscz.dup19, gscz_gwas)
sczdup  <- cbind(as.data.frame(gscz.dup19, row.names=NULL), as.data.frame(gscz_gwas[near], row.names=NULL))
sczdup[,c(3,4,5,12,14,15,16)] <- NULL
colnames(sczdup)[c(2,9)] <- c("start_cnv", "start_snp")
sczdup$distance <- cut(abs(sczdup$start_cnv-sczdup$start_snp),c(-1,1,10,100,1000,100000,1E8))
table(sczdup$distance)
ggplot(sczdup[sczdup$distance=="(-1,1]",], aes(x=z, y=or)) + geom_point(alpha=0.1)
tb <- table(sczdup$z>0, sczdup$or>1)
chisq.test(tb)

```

```{r sanity}
near <- nearest(gscz_gwas, gheight_gwas)
snp  <- cbind(as.data.frame(gscz_gwas, row.names=NULL), as.data.frame(gheight_gwas[near], row.names=NULL))
head(snp)
snp[,c(3,4,5,8,10,11,12)] <- NULL
colnames(snp)[c(2,4,5,7)] <- c("start_scz","p_scz","start_h", "p_h")

chisq.test(table(snp$p_scz<0.0001,snp$p_h<0.0001))

csq <- chisq.test(table(snp$b>0, snp$or>1))


snp$distance <- cut(abs(snp$start_scz-snp$start_h),c(-1,1,10,100,1000,100000,1E8))
table(snp$distance)
ggplot(snp[snp$distance=="(-1,1]",], aes(x=b, y=or, col=factor((p_scz<0.0001)+2*(p_h<0.0001)))) + geom_point(alpha=0.05) + guides(colour = guide_legend(override.aes = list(alpha = 1))) 
```