---
title: "Schizophrenia and Height CNV"
output: html_notebook
---

```{r prepare, echo=FALSE, cache=TRUE}
setwd("D:/Ian/IHG/projects/CNVIntolerance/Examples")   ## You would need to change to the directory where your file is stored
source("helper_functions.R")
install.load("pander", "ggplot2", "data.table")

## Read the non-gene centric results.
scz.dup <- read.table("C:\\Users\\nijw\\Dropbox/CNVIntolerance/pgc_cnv/PGC_41K_QC_dup.cnv.results", header=TRUE)
scz.del <- read.table("C:\\Users\\nijw\\Dropbox/CNVIntolerance/pgc_cnv/PGC_41K_QC_del.cnv.results", header=TRUE)
gscz.dup <- GRanges(seqnames=scz.dup$CHR, IRanges(start=scz.dup$BP, width=1), z=scz.dup$z, p=scz.dup$z_pval)
gscz.del <- GRanges(seqnames=scz.del$CHR, IRanges(start=scz.del$BP, width=1), z=scz.del$z, p=scz.del$z_pval)

#
height <- fread("C:\\Users/nijw/Dropbox/CNVIntolerance/height_CNV_association_41467_2017_556_MOESM2_ESM.csv")
height_hg19 <- fread("C:\\Users/nijw/Dropbox/CNVIntolerance/cnv_hg19.bed")
height_hg19[,V3:=NULL]
colnames(height_hg19) <- c("CHR", "BP", "ID")
height$ID <- paste("ID", height$CHR, height$BP, sep="_")
setkey(height, ID)
setkey(height_hg19, ID)

h <- height_hg19[height]
h[, ID := NULL]
h[,CHR := i.CHR]
h[,i.CHR := NULL]
h[,i.BP := NULL]


height_raw <- fread("C:\\Users/nijw/Dropbox/CNVIntolerance/cnv_catalogue_CNVs_2018-01-24_03_51_11.csv")

#check <- cbind(height_raw$BP, height$BP, height_raw$BP -  height$BP )
#check[1:10,]

h3 <- merge(height_raw, h, by=c("CHR", "BP"))
height_cnv19 <- h3

plot(h3$F_DUP.x, h3$F_DUP.y)

head(scz.del)
head(height)

save(height_cnv19, file="height_cnv19.rda")   ## saved so I don't have to go through this again

gheight_cnv19 <- GRanges(height_cnv19$CHR, IRanges(height_cnv19$BP, width=1), 
                         p = height_cnv19$`Pvalue Weight`, beta= height_cnv19$`Beta Height`)

```

We have read `r nrow(scz.del)` rows of deletions and `r nrow(scz.dup)` rows of duplications for schizophrenia and `r nrow(height)` for the height study.



The schizophrenia data are based on  cohort of 21,094 cases and 20,227 controls, giving a total sample 
size of 41,321. These were *A final set of rare, highquality CNVs was defined as those >20 kb in length, encompassing at
least 10 probes and <1% minor allele frequency (MAF). *

#### Height

*Depending on the trait, the sample sizes varied between 161,244 and 191,161.*

There seems to be a major problem witt the height CNVs.  A proportion of these have frequencies greater than 1.   This is the same for the database frequencies that are on the web site.



```{r}

a <- rbind(
  data.frame(n=scz.del$NCNV, type="del"),
  data.frame(n=scz.dup$NCNV, type="dup"))

a$freq <- a$n/41321

a$cut <- cut(a$n, breaks=c(0,1,2,5,10,20,50,100,1000) )
tb <- table(n=a$cut,type=a$type )
tbf <- as.data.frame(tb)
pander(tb)
ggplot(tbf, aes(y=Freq, x=n, col=type)) + geom_point()
ggplot(a, aes(x=n, col=type)) + geom_density() + scale_x_log10()

plot(density(a$freq))
```

## Overlaps between scz, and height

```{r}
o <- nearest(gheight_cnv19, gscz.dup)
res <- cbind(data.frame(gheight_cnv19), data.frame(gscz.dup[o]) )
nrow(res)
u <- abs(res[,2] - res[,9])<10000
resb <- res[u,]
hist(resb[,2]-resb[,9])
nrow(resb)
resb$strand <- NULL
resb$strand <- NULL

colnames(resb) <- c("seqnames","start_h","end_h","width_h","p_h","beta_h","seqnames_s","start_s","end_s","width_s","z","p_s")
ggplot(resb, aes(x=beta_h, y=z, col=factor((p_s<0.01)  +2*(p_h<0.01)))) + geom_point(alpha=0.03)
```

### The same with deletions


```{r}
o2 <- nearest(gheight_cnv19, gscz.del)
res2 <- cbind(data.frame(gheight_cnv19), data.frame(gscz.del[o2]) )
nrow(res2)
u2 <- abs(res2[,2] - res2[,9])<10000
res2b <- res2[u2,]
hist(res2b[,2]-res2b[,9])
nrow(res2b)
res2b$strand <- NULL
res2b$strand <- NULL

colnames(res2b) <- c("seqnames","start_h","end_h","width_h","p_h","beta_h","seqnames_s","start_s","end_s","width_s","z","p_s")
ggplot(res2b, aes(x=beta_h, y=z, col=factor((p_s<0.01)  +2*(p_h<0.01)))) + geom_point(alpha=0.03)
```
